External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-08 CVPR2017_Review_Unified.tex
add

The external priors in natural clean images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and priors of internal. In this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups of given noisy image, and internal orthogonal dictionary learning (DL) for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising. Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.

@@

In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem. In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussians to estimate the noise covariance matrix and latent clean images in wavelet domain. The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called ``Noise Clinic" \cite{noiseclinic,ncwebsite}. This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explict distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is time consumming.

@@

Natural images often demonstrate repetitive local patterns, this nonlocal self-similarity (NSS) property is a key successful factor for many image denoising methods \cite{nlm,bm3d,lssc,wnnm,pgpd}. In this section, we formulate the Patch Group prior learned on natural color images. Similar to \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch. The patch group mean is subtracted, and hence different groups of patches can share similar PGs. In this way, the space natural image patches to be modeled is largely reduced.

@@

The comparisons are performed on two standard datasets in which the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings. The first dataset provided in \cite{crosschannel2016} includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed. Since the 17 images share repetitive contents, we cropped them into 60 smaller images (of size $500\times 500\times3$) including different contents. Some samples are shown in Figure \ref{fig4}. We also perform comparison on the 15 cropped images (of size $512\times 521\times3$) used in \cite{crosschannel2016}. Noted that the noise in the 15 images used in \cite{crosschannel2016} is different from the noise in the 60 images cropped from \cite{crosschannel2016} since they are taken in different shots. The second dataset provided in \cite{ncwebsite} includes about 20 real noisy images collected under uncontrolled outdoor environment. This dataset does not have ``ground truth" images.

@@

\subsection{Comparison with External and Internal Priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal"). The three methods perform denoising under the same framework as Eqn. (\ref{equ5}). The ``External" method employs the external dictionaries (i.e., $r=0$ in Eqn. (\ref{equ5})) for denoising, while the ``Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Eqn. (\ref{equ5})). All parameters of the three methods are tuned to achieve best performance.

>>>>

The external priors in natural clean images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and priors of internalwould naturally achieves better performance. In this paper, we propose to employ the external priors learned from natural clean images to guide the learning of internal priors of given noisy image. We learn the external priors of patch groups \cite{pgpd} since nonlocal self-similarity is successfully used in many denoising methods \cite{nlm,bm3d,wnnm,pgpd}. The learning of external priors is performed by Gaussian Mixture Model. The learning of internal priors includes Gaussian selection and orthogonal dictionary learning (DL). The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. The real noisy image denoising is simultaneously done with the DL process. Both of the two stages have closed-form solutions. Hence, our proposed denoising method is very efficient. Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.

@@

In the last decade, researchers proposed many methods \cite{fullyblind,rabie2005robust,Liu2008,almapg,noiseclinic,ncwebsite,Zhu_2016_CVPR,crosschannel2016} for real image denoising problem. In \cite{fullyblind}, Portilla proposed to use scale mixture of Gaussians to estimate the noise covariance matrix and latent clean images in wavelet domain. The work of Rabie \cite{rabie2005robust} modeled the noisy pixels as outliers which are removed via Lorentzian robust estimator \cite{huber2011robust}. Liu \etal \cite{Liu2008} proposed to use ``noise level function" to estimate the noise and then use Gaussian conditional random field to obtain the latent clean image. Gong et al. \cite{almapg} m odels the noise by mixed $\ell_{1}$ and $\ell_{2}$ norms and remove the noise by sparsity prior in the wavelet transform domain. Later, Lebrun el al. proposed a multiscale denoising algorithm called ``Noise Clinic" \cite{noiseclinic,ncwebsite}. This method generalizes the NL-Bayes model \cite{nlbayes} to deal with blind noise and achieves state-of-the-art performance. Recently, Zhu et al. proposed a Bayesian model \cite{Zhu_2016_CVPR} which approximates and removes the noise via low-rank mixture of Gaussians. However, these methods largely depends on the modeling of noise in real noisy images which is hard to be modeled by explict distributions. Besides, the parametric estimation of the Gaussian or MoG distribution is often time consumming \cite{B}.

@@

In this section, we formulate the Patch Group prior learned on natural color images. Similar to \cite{pgpd}, the patch group (PG) is defined as a group of similar patches to the local patch. The patch group mean is subtracted, and hence different groups of patches can share similar PGs. In this way, the space natural image patches to be modeled is largely reduced.

@@

The comparisons are performed on two standard datasets in which the images were captured under indoor or outdoor lighting conditions by different types of cameras and camera settings. The first dataset provided in \cite{ncwebsite} includes 20 real noisy images collected under uncontrolled outdoor environment. This dataset does not have ``ground truth" images and hence the objective measurements can not be performed. In order to evaluate the compared methods on quantitative measures, we perform experiments on the second dataset provided in \cite{crosschannel2016}. It includes 17 real noisy images and corresponding mean images. The noisy images were collected under controlled indoor environment. Some samples can be found in \cite{crosschannel2016}. For each image, the same scene was shot 500 times under the same camera and camera setting. The mean image of the 500 shots is roughly taken as the ``ground truth", with which the PSNR can be computed. Since the 17 images are too large (of size about $7000\times5000\times3$) and share repetitive contents, the authors in \cite{crosschannel2016} performed comparison on 15 cropped images (of size $512\times 521\times3$). To evaluate the compared methods on more samples, we cropped the 17 large images from \cite{crosschannel2016} into 60 smaller images (of size $500\times 500\times3$) including different contents. Some samples are shown in Figure \ref{fig4}. Note that the noise in our cropped 60 images used in \cite{crosschannel2016} are different from the noise in the 15 images cropped by the authors of \cite{crosschannel2016} since they are taken in different shots.

@@

\subsection{Comparison among external, internal and external guided internal priors}
In this section, we compare our proposed method on real image denoising with external prior based method (denoted as ``External") and internal prior based method (denoted as ``Internal"). The three methods perform denoising under the same framework as Eqn. (\ref{equ5}). The ``External" method employs the external dictionaries (i.e., $r=0$ in Eqn. (\ref{equ5})) for denoising, while the ``Internal" method employ the GMM (also with $K=32$ Gaussians) to directly cluster the internal noisy PGs into multiple subspaces, and for each subspace perform denoising with fully learned dictionary (i.e., $r=3p^{2}$ in Eqn. (\ref{equ5})). All parameters of the three methods are tuned to achieve best performance.
